Experiment 2

### 2021-07-09 experiments/experiment 1/experiment 1.Rmd
figures and results to discuss
Change installation of microxanox in experiments

# remotes::install_github(
#   "opetchey/microxanox",
#   ref = microxanox_release,
#   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
#   build_vignettes = FALSE,
#   force = TRUE,
#   upgrade = FALSE,
#   lib = tmplib
# )

#library(microxanox, lib.loc = tmplib)

@@

```{r}
options(mc.cores = 6)
```

>>>>

# remotes::install_github(
#   "UZH-PEG/microxanox",
#   ref = "0.2",
#   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
#   build_vignettes = FALSE,
#   force = TRUE,
#   upgrade = FALSE
# )

@@

```{r}
options(mc.cores = 4)
```

### 2021-07-09 experiments/experiment 2/experiment 2.Rmd
figures and results to discuss
Change installation of microxanox in experiments

# remotes::install_github(
#   "opetchey/microxanox",
#   ref = microxanox_release,
#   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
#   build_vignettes = FALSE,
#   force = TRUE,
#   upgrade = FALSE,
#   lib = tmplib
# )

>>>>

# remotes::install_github(
#   "UZH-PEG/microxanox",
#   ref = "0.2",
#   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
#   build_vignettes = FALSE,
#   force = TRUE,
#   upgrade = FALSE
# )
